\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-11-25 papers/jss/article.Rnw
three small edits
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@907 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

Protocol Buffers are a modern, language-neutral, platform-neutral,
extensible mechanism for sharing and storing structured data.  Some of
the key features provided by Protocol Buffers for data analysis include:

@@

After importing proto files, the corresponding message descriptors are
available by name from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.  This allows new descriptors to be
parsed from \code{.proto} files and added to the global
namespace.\footnote{Note that there is a significant performance
  overhead with this RObjectTable implementation.  Because the table
  is on the search path and isn't cacheable, lookups of symbols that
  are behind it in the search path can't be added to the global object
  cache, and R must perform an expensive lookup through all of the
  attached environments and the protocol buffer definitions to find common
  symbols (most notably those in base) from the global environment.
  Fortunately, proper use of namespaces and package imports reduces
  the impact of this for code in packages.}

@@

Table~\ref{class-summary-table} lists the six primary Message and
Descriptor classes in \pkg{RProtoBuf}.
Please see the package
documentation for a complete description of the slots and methods for
each class.

>>>>

Protocol Buffers are a modern, language-neutral, platform-neutral,
extensible mechanism for sharing and storing structured data.  Some of
the key features provided by Protocol Buffers for data analysis are:

@@

After importing proto files, the corresponding message descriptors are
available by name from the \code{RProtoBuf:DescriptorPool} environment in 
the \proglang{R} search path.  This environment is implemented with the 
user-defined tables framework from the \pkg{RObjectTables} package
available from the OmegaHat project \citep{RObjectTables}.  Instead of
being associated with a static hash table, this environment
dynamically queries the in-memory database of loaded descriptors
during normal variable lookup.  This allows new descriptors to be
parsed from \code{.proto} files and added to the global
namespace.\footnote{Note that there is a significant performance
  overhead with this RObjectTable implementation.  Because the table
  is on the search path and isn't cacheable, lookups of symbols that
  are behind it in the search path cannot be added to the global object
  cache, and R must perform an expensive lookup through all of the
  attached environments and the protocol buffer definitions to find common
  symbols (most notably those in base) from the global environment.
  Fortunately, proper use of namespaces and package imports reduces
  the impact of this for code in packages.}

@@

Table~\ref{class-summary-table} lists the six primary Message and
Descriptor classes in \pkg{RProtoBuf}.
The package documentation provides a complete description of the slots and methods for
each class.
